Manuscript_Github_Pchabaudi_pir

### 2022-07-26 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Move through GO enrichment analysis

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')
library('ComplexHeatmap')
library('circlize') # for circular plots and colour
library("factoextra")
library("MatrixGenerics") # for rowMins and rowMax

@@

```{r phase_go_enrich}
#Get the gene list for each group of genes in and out of phase.
z_max_diff.list <- lapply(seq(0,4), 
                          function(diff_num) filter(z_max_diff, diff == diff_num) %>% 
                            .$Geneid)
names(z_max_diff.list) <- seq(0,4)
```

>>>>

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')
library('ComplexHeatmap')
library('circlize') # for circular plots and colour
library("factoextra")
library("MatrixGenerics") # for rowMins and rowMax
library("topGO")
library("FoldGO")

@@

```{r phase_go_enrich}
#Get the gene list for each group of genes in and out of phase.
gene.list <- chabaudi_gene_info$Geneid
z_max_diff.list <- lapply(seq(0,4), 
                          function(diff_num) {
                            diff.list <- filter(z_max_diff, diff == diff_num) %>% 
                              .$Geneid
                            #Get 1 for on the list and 0 for not.
                            gene_diff.list <- as.integer(gene.list %in% diff.list)
                            names(gene_diff.list) <- gene.list
                            return(gene_diff.list)
                          })
names(z_max_diff.list) <- seq(0,4)

#Read in the GO-Annotation file using GAFReader from FoldGO.
# getAnnotation to obtain a list of the GO terms and associated genes.
# inverseList (from topGO) to turn this into list of geneID with associated GO terms.
gaf <- GAFReader("../standard_files/PlasmoDB-48_Pchabaudichabaudi_GO.gaf")
go_annotation <- inverseList(getAnnotation(gaf))

#Make a topGOdata object 
GOdata <- new("topGOdata", 
              ontology = "CC", 
              geneSel = function(x){x == 1},
              allGenes = z_max_diff.list$`0`,
              annot = annFUN.gene2GO, 
              gene2GO = go_annotation)
